One-shot learning: From domain knowledge to action models

### 2019-02-19 doc/ijcai-19-deductivelearning/deductivelearning.tex
added new conditional effects table to ijcai19 paper on deductive leaarning

Figure~\ref{fig:ceffects} summarizes the new conditional effects added to the classical planning compilation for the learning of \strips\ action models from {\em schematic mutex}. Next we describe each of them in detail:
\begin{enumerate}
\item[1-3.] For every {\em schematic mutex} $\tup{p,q}$ s.t. both $p$ and $q$ belong to $\in{\mathcal I}_{\Psi,\xi}$ a conditional effect is added to the $\mathsf{insertPre_{p,\xi}}$ actions to ban the insertion of two preconditions that are {\em schematic mutex}. Likewise, two conditional effects are added to the $\mathsf{insertEff_{p,\xi}}$ actions to ban the insertion of two positive/negative effects that are {\em schematic mutex}.
\item[4-5.] For every {\em schematic mutex} $\tup{p,q}$ s.t. both $p$ and $q$ belong to $\in{\mathcal I}_{\Psi,\xi}$ two conditional effects are added to the $\mathsf{apply_{\xi,\omega}}$ actions to ban a positive effect that is inconsistent with an input observation.
\end{enumerate}

\begin{figure}
\begin{tabular}{lll}
{\bf ID} & {\bf Action} & {\bf New conditional effect}\\\hline
1.& $\mathsf{insertPre_{p,\xi}}$ & $\{pre\_q\_\xi\}\rhd\{mode_{inval}\}$\\
2.& $\mathsf{insertEff_{p,\xi}}$ & $\{pre\_q\_\xi,eff\_q\_\xi,pre\_p\_\xi\}\rhd\{mode_{inval}\}$\\
3.& $\mathsf{insertEff_{p,\xi}}$ & $\{\neg pre\_q\_\xi,eff\_q\_\xi,\neg pre\_p\_\xi\}\rhd\{mode_{inval}\}$\\
5.& $\mathsf{apply_{\xi,\omega}}$ & $\{\neg pre\_p\_\xi \wedge eff\_p\_\xi \wedge $\\
& & $q(\omega)\wedge \neg pre\_q\_\xi\}\rhd\{mode_{inval}\}$\\
6.& $\mathsf{apply_{\xi,\omega}}$ & $\{\neg pre\_p\_\xi \wedge eff\_p\_\xi \wedge $\\
& &$q(\omega)\wedge pre\_q\_\xi \wedge \neg eff\_q\_\xi\}\rhd\{mode_{inval}\}$
\end{tabular}
	\caption{\small Summary of the new conditional effects added to the classical planning compilation for the learning of \strips\ action models.}
	\label{fig:ceffects}
\end{figure}

>>>>

Figure~\ref{fig:ceffects} summarizes the new conditional effects added to the classical planning compilation for the learning of \strips\ action models from {\em schematic mutex}. Next we describe each of them in detail:
\begin{enumerate}
\item[1-3.] For every {\em schematic mutex} $\tup{p,q}$ s.t. both $p$ and $q$ belong to $\in{\mathcal I}_{\Psi,\xi}$ a conditional effect is added to the $\mathsf{insertPre_{p,\xi}}$ actions to ban the insertion of two preconditions that are {\em schematic mutex}. Likewise, two conditional effects are added to the $\mathsf{insertEff_{p,\xi}}$ actions to ban the insertion of two positive/negative effects that are {\em schematic mutex}.
\item[4-5.] For every {\em schematic mutex} $\tup{p,q}$ s.t. both $p$ and $q$ belong to $\in{\mathcal I}_{\Psi,\xi}$ two conditional effects are added to the $\mathsf{apply_{\xi,\omega}}$ actions to ban positive effects that are inconsistent with an input observation.
\end{enumerate}

\begin{figure}
\begin{tabular}{lll}
{\bf ID} & {\bf Action} & {\bf New conditional effect}\\\hline
1.& $\mathsf{insertPre_{p,\xi}}$ & $\{pre\_q\_\xi\}\rhd\{mode_{inval}\}$\\
2.& $\mathsf{insertEff_{p,\xi}}$ & $\{pre\_q\_\xi,eff\_q\_\xi,pre\_p\_\xi\}\rhd\{mode_{inval}\}$\\
3.& $\mathsf{insertEff_{p,\xi}}$ & $\{\neg pre\_q\_\xi,eff\_q\_\xi,\neg pre\_p\_\xi\}\rhd\{mode_{inval}\}$\\
4.& $\mathsf{apply_{\xi,\omega}}$ & $\{\neg pre\_p\_\xi \wedge eff\_p\_\xi \wedge $\\
& & $q(\omega)\wedge \neg pre\_q\_\xi\}\rhd\{mode_{inval}\}$\\
5.& $\mathsf{apply_{\xi,\omega}}$ & $\{\neg pre\_p\_\xi \wedge eff\_p\_\xi \wedge $\\
& &$q(\omega)\wedge pre\_q\_\xi \wedge \neg eff\_q\_\xi\}\rhd\{mode_{inval}\}$
\end{tabular}
	\caption{\small Summary of the new conditional effects added to the classical planning compilation for the learning of \strips\ action models.}
	\label{fig:ceffects}
\end{figure}
